\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme{banking}
\moderncvcolor{blue}
\moderncvstyle[]{banking}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[margin=1.8cm]{geometry}
\usepackage[sfdefault, light]{roboto}

% Customizations

\input{moderncvcustom}
\renewcommand{\baselinestretch}{1.45}
\def\arraystretch{1.2}
\setlength\parindent{1.5em}
\nopagenumbers 

% Settings

\IfFileExists{information-secrete}{
  \input{information-secrete}
}{
  \input{information-public}
}

% Some better tables with custom alignments

\usepackage{tabularx}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

% Footer with initials and page count

\usepackage{lastpage}
\lfoot{\addressfont\itshape\textcolor{gray}{\tiny AVW}}
\rfoot{\addressfont\itshape\textcolor{gray}{\tiny Page \thepage\ of \pageref{LastPage}}}

% --------
% Document
% --------

\begin{document}

\recipient{To whom it may concern}{Siemens Mobility GmbH\\Erlangen, Germany}
\date{\today}

\opening{Dear Sir or Madam,}
\closing{Kind regards,}
\coversubject{Application for the role of Project Manager, Embedded Linux systems in locomotives (job \#425576)}

\makeletterhead

While I realise the job description likely calls for a more junior candidate, I would like to express my strong interest for the position of Project Manager for embedded Linux systems in locomotives. I have spent the last 5 years working as a Senior Project lead and Team lead for an interdisciplinary engineering team designing and building hardware solutions for Railway remote condition monitoring systems (track side) and I would be thrilled to pursue my commitment to bringing new technologies to the rail/mobility industry at Siemens Mobility together with my passion for embedded systems. One of the main reasons driving me to search for a new opportunity at this time is a silver-lining across my entire career: I have always valued expanding my technical knowledge and field of application, as well as finding an environment where peers exchange their knowledge and expertise in an effort to elevate both contributors and leaders of an organisation. This is sadly absent from my current role.

\vspace{1em}
\par\noindent Having worked in the semiconductor business, automotive-adjacent industry and more recently in the railway industry over the last 13 years, I am familiar with the intricate requirements and needs for transparency and clarity that emerge from complex cross-functional and long-term projects. I am versed in product design and driving a roadmapping process as well as portfolio, risk, and customer management and I do my best work when I am able to discuss and distil these high-level concepts directly with the engineering team to agree on a detailed breakdown of what I like to distinguish between `product backlog` and `small actionable items`, though we can just call these a backlog.

\vspace{1em}
\par\noindent Ideally, I would like to find a role that remains close to the technology as much as to the individual contributors. I think a backlog is only a small fraction of the deliverables a project manager can provide an organisation and an engineering team with, especially in the embedded systems domains. I find that very close collaboration with the engineering team(s) is paramount to accurate and realistic project plans and estimates, while consistent communication with stakeholders allows for more agility and flexibility.

\vspace{1em}
\par\noindent I would be delighted to discuss this further should you find my expertise relevant and thank you for considering my application. I remain at your disposal for any further information.

\makeletterclosing


\end{document}